Project-I by Group Sydney

### 2015-10-24 report/paper.tex
Fix bug RMSE

In order to evaluate our different models, we first have split our data ($\mathbf{X}$) in two sets of $80\%$ and $20\%$, for the training and the test sets. We choose this percentage in order to have still enough data for the training set and also enough in order to estimate correctly our models on the testing set with a concrete size. We learn with our models only on the training set and use the test set in order to estimate the error using the \textit{Root Mean Square Error}. Moreover, we have also used k-cross validation (see next section for the values of k) to tune the parameters like lambda of the different polynomial degrees. We repeated the experiment $100$ times with different seed in order to split the data in a unique random way for each trial. Finally, we made varied the lambda from $10^{-5}$ to $10^{5}$ with $500$ values between.

@@

>>>>

In order to evaluate our different models, we first have split our data ($\mathbf{X}$) in two sets of $80\%$ and $20\%$, for the training and the test sets. We choose this percentage in order to have still enough data for the training set and also enough in order to estimate correctly our models on the testing set with a concrete size. We learn with our models only on the training set and use the test set in order to estimate the error using the \textit{Root Mean Square Error}. Moreover, we have also used k-cross validation (see next section for the values of k) to tune the parameters like lambda of the different polynomial degrees. We repeated the experiment $30$ times with different seed in order to split the data in a unique random way for each trial. Finally, we made varied the lambda from $10^{-5}$ to $10^{5}$ with $500$ values between.

@@

\begin{figure}[!t]
\center
\includegraphics[width=6in]{figures/models.jpg} \label{fig:models}
\caption{Boxplot of our models, using the RMSE. Each model is represented with a box where we can see their mean and their standard deviation.}
\end{figure}
